\propertitle

### 2019-06-13 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-12T20:30:19+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Regarding point~\ref{item:maxent_step}, we assume the reader to be familiar
with the maximum-entropy method. In short, it amounts to choosing the
distribution having maximum Shannon entropy among those satisfying specific
convex constraints, such as expectation values. We add two remarks. First,
the \enquote{distribution} given by this method is the zeroth-order
approximation of four different distributions:
\begin{itemize}
\item the \emph{probability} distribution for the value of the activity at any
  time bin among those \emph{recorded},
\item the \emph{probability} distribution for the value of the activity at
  a \emph{new} time bin,
\item the most probable \emph{time-frequency} distribution of the activity
  during the \emph{recording},
\item the most probable \emph{time-frequency} distribution of the activity
  in a very long run of \emph{new} time bins.
\end{itemize}
So the maximum-entropy \enquote{distribution} is an approximate answer to
four conceptually different inferences. Note that although these four
distributions numerically coincide in this approximation, they numerically
differ in higher-order approximations. Second, the maximum-entropy method
based on the Shannon entropy implicitly makes specific assumptions about
the probability of the long-run frequency distributions
\citep{jaynes1986d_r1996,portamana2009,portamana2017}. We discuss these
assumptions in \sect***

In our case, to apply the method to the total activity of the full
population we need to set some of its expectation values, for example its
moments. Here enters point~\ref{item:sample_step}:

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-13T11:51:25+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

Regarding point~\ref{item:maxent_step}, we assume you to be familiar with
the maximum-entropy method. In short, it amounts to choosing the
distribution having maximum Shannon entropy among those satisfying specific
convex constraints, such as expectation values; these expectations are
typically chosen to be equal to measured averages. We add two remarks that
you may not be familiar with. First, the \enquote{distribution} given by
this method is the zeroth-order approximation of four different
distributions:
\begin{itemize}
\item the \emph{probability} distribution for the value of the activity at any
  time bin among those \emph{recorded},
\item the \emph{probability} distribution for the value of the activity at
  a \emph{new} time bin,
\item the most probable \emph{time-frequency} distribution of the activity
  during the \emph{recording},
\item the most probable \emph{time-frequency} distribution of the activity
  in a very long run of \emph{new} time bins.
\end{itemize}
The maximum-entropy distribution is thus an approximate answer to four
conceptually different inferences. Note that although the four
distributions above numerically coincide in this approximation, they
numerically differ in higher-order approximations. Second, the
maximum-entropy method based on the Shannon entropy implicitly makes
specific assumptions about the probability of the long-run frequency
distributions \citep{jaynes1986d_r1996,portamana2009,portamana2017}. We
discuss these assumptions in \sect***

In our case, to apply the method to the total activity of the full
population we need to fix some of its expectation values, for example its
moments. But we don't have any measured averages for the full population to
equate our expectations to. Here enters point~\ref{item:sample_step}:
classical sampling theory
\citep[for example][\chaps~I--IV]{whitworth1867_r1965}[\chap~II]{feller1950_r1968}[\chap~3]{jaynes1994_r2003}[see
also][]{whitworth1897}.
